Modeling Galaxy Spectral Energy Distributions in the SDSS Spectroscopic Survey

### 2002-02-05 docs/paper/paper.tex
Hogg tweaks
git-svn-id: svn+ssh://howdy.physics.nyu.edu/usr/local/svn/kcorrect/trunk@19 75dff457-8751-0410-ab1a-cd701654ce6b

In the future, all observations of galaxies (and indeed of the sky in
general) will be performed using integral field spectrographs or
equivalent devices which combine high spatial resolution, high
spectral resolution, and high signal-to-noise. By that time, the
phenomenon of broad-band filters and the quaint nomenclature
surrounding their usage --- magnitudes, $K$-corrections, color terms,
{\it etc.} --- will have long since been forgotten. However, today
virtually all observations of galaxies are made through such filters,
and special care has to be taken to recover knowledge of galaxy
spectral energy distributions (SEDs) from these observations. This
paper describes how to do so in a way well-suited for recovering (for
example) fixed-frame magnitudes of objects over a large range of
redshifts.

>>>>

In the future, observations of galaxies (and indeed of any
astronomical sources) will be performed using integral field
spectrographs or equivalent devices which combine high spatial
resolution, high spectral resolution, and high signal-to-noise. By
that time, the phenomena of broad-band filters and the quaint
terminology surrounding their usage --- magnitudes, $K$-corrections,
color terms, {\it etc.} --- will have long since been
forgotten. However, today, virtually all observations of galaxies are
made through such filters, and special care has to be taken to recover
knowledge of galaxy spectral energy distributions (SEDs) from these
observations. This paper describes how to do so in a way well-suited
for recovering (for example) fixed-frame magnitudes of objects over a
large range of redshifts.
